---
title: "R Bridge Week 3 Assignment"
author: "Steven Han"
date: "`r Sys.Date()`"
fontsize: 8
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

***
### Question
In probability, $_nC_r$ means $\frac{n!}{( n - r)! * r!}$. For example, $_5C_3$ evaluates to 10.

R has built in functions for `choose()` and `factorial()`. Your task is to write your own variation of the `choose()` function, that does not use either of these functions.

Your code should adhere to the [style guidelines](http://adv-r.had.co.nz/Style.html) provided by Hadley Wickham in this week's reading.  You need to create your code and some test code, and deliver your code, results, and documentation in a single R Markdown file.

***

### Helper Function
```{r}
# Create a helper function, calc_fact, to calculate the factorials within the combination

calc_fact <- function(num) {
    if(num == 0)
    {
        return(1)
    }
    else return(num * calc_fact(num - 1))
}
```

### Combination Function Using the Helper Function
```{r}
# The calc_combination function will first elimnate base cases before evaluating the result.

calc_combination <- function(set_total, set_subset) {
    if (set_subset > set_total || set_subset < 0 || set_total < 0) {
        return(0)
    } else if (set_subset == set_total || set_subset == 0) {
        return(1)
    } else {
        numerator = calc_fact(set_total)
        denominator = calc_fact(set_total - set_subset) * calc_fact(set_subset)
        return(numerator / denominator)
    } 
}
```

***

### Code Evaluation
Let us now test our function. For a simple example, we will consider a set of three fruits--apple, banana, and orange--and see how many unordered sets of 2 we can create.

* apple, banana
* apple, orange
* banana, orange

In this example, we can create 3 sets of 2 from our total set of 3. Now let's use our `calc_combination()` function to see if we get the same result:

```{r}
calc_combination(3,2)
```

We will now evaluate whether the above code works correctly by evaluating the results of` calc_combination()` with the `choose()` R base function[^1].

```{r results='asis', echo=FALSE}
set_total_nums <- c(5, 10, 2, 15)
set_subset_nums <- c(3, 0, 4, 7)
our_answers <- c(calc_combination(5, 3), calc_combination(10, 0), calc_combination(2, 4), calc_combination(15, 7))
r_answers <- c(choose(5, 3), choose(10, 0), choose(2, 4), choose(15, 7))
ans_results <- our_answers == r_answers
table_results <- data.frame("Set_Total"=set_total_nums, "Subset"=set_subset_nums, "calc_combination"=our_answers, "choose"=r_answers, "Validation"=ans_results)

knitr::kable(table_results, align = 'c')
```

```{r results='asis', echo = FALSE, eval=FALSE}

## Hidden R Code
## Testing a nested for loop and the do.call function for traversing through test cases

func_vector <- c("calc_combination", "choose")
set_total_nums <- c(5, 10, 2, 15)
set_subset_nums <- c(3, 0, 4, 7)
table_results <- data.frame(Set_Total=as.numeric(), Subset=as.numeric(), calc_combination=as.numeric(), choose=as.numeric(), Validation=as.logical())

for (i in 1:length(set_total_nums)) {
    table_results[i, "Set_Total"] <- set_total_nums[i]
    table_results[i, "Subset"] <- set_subset_nums[i]
    
    for (n in 1:length(func_vector)) {
         table_results[i, func_vector[n]] <- do.call(func_vector[n], args = list(set_total_nums[i], set_subset_nums[i]))
    }
    table_results[i, "Validation"] <- length(unique(t(table_results[i, func_vector]))) == 1
}

knitr::kable(table_results, align = 'c')
```

***

[^1]: While the `calc_combination()` function assumes that there can be no negative set totals, in reality, `choose()` will return a real number when the set total is less than zero. 